R Notebook

### 2024-06-06 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
fb

# merge two data frames by ID 
df_merge <- merge(df_demo,
                  df_rating,
                  by = "ID") %>% 
  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
                    "132")
         )

@@

# single bpm values 
main_single_hr <-
map(.x = dir(path = data_path,
             pattern = ".csv"),
    ~ read_csv(file.path(data_path, .), 
               id = "id",
               col_types = c("t","n")
               ) %>% 
  mutate(time = .$Time - min(.$Time),
         time = as.numeric(time),
         heart_rate = `Heart Rate`,
         ID = id,
         time_span = case_when(str_detect(string = id, pattern = "_a") ~ "end",
                               str_detect(string = id, pattern = "_m") ~ "teaching",
                               str_detect(string = id, pattern = "_p") ~ "preparation",
                               str_detect(string = id, pattern = "_s") ~ "post",
                               str_detect(string = id, pattern = "_i") ~ "interview",
                               TRUE ~ "overall"
                               ),
         ID = str_extract(string = ID,
                          pattern = "[:digit:]{3}"),
         ID = as.numeric(ID)
      ) %>%
    # filter(time <= 600) %>% # filter for 10min intervals
    filter(time <= 7200) %>% # filter for 2 hours (maximal duration of study)
    dplyr::select(!c("Time","Heart Rate","id"))
    ) %>%
  bind_rows()

# multiple bpm values
# 
# main_single_hr <-
#   left_join(main, 
#             df_demo,
#             by = "ID")
# 
# main_single_hr <- 
#   main_single_hr %>% 
#   dplyr::select("time", "heart_rate", "ID", "time_span") %>% 
#   distinct() %>% 
#   group_by(ID) %>% 
#   dplyr::summarise(mean_heart = mean(heart_rate),
#             sd_heart = sd(heart_rate)) %>%
#   ungroup() %>% 
#   right_join(x = .,
#              y = main,
#              by = "ID") %>% 
#   filter(!(time_span == "teaching" & time > 600)) %>%
#   mutate(heart_rate_std = (heart_rate - mean_heart)/
#            sd_heart)
# 
# main_single_hr <-
# map(.x = dir(path = data_path,
#              pattern = ".csv"),
#     ~ read_csv(file.path(data_path, .), 
#                id = "id",
#                col_types = c("t","n")
#                ) %>% 
#   mutate(time = .$Time - min(.$Time),
#          time = as.numeric(time),
#          heart_rate = `Heart Rate`,
#          ID = id,
#          time_span = case_when(str_detect(string = id, pattern = "_a") ~ "end",
#                                str_detect(string = id, pattern = "_m") ~ "teaching",
#                                str_detect(string = id, pattern = "_p") ~ "preparation",
#                                str_detect(string = id, pattern = "_s") ~ "post",
#                                str_detect(string = id, pattern = "_i") ~ "interview",
#                                TRUE ~ "overall"
#                                ),
#          ID = str_extract(string = ID,
#                           pattern = "[:digit:]{3}"),
#          ID = as.numeric(ID)
#       ) %>%
#     # filter(time <= 600) %>% # filter for 10min intervals
#     filter(time <= 7200) %>% # filter for 2 hours (maximal duration of study)
#     dplyr::select(!c("Time","Heart Rate","id"))
#     ) %>%
#   bind_rows()
# 
# 
# main <-
#   left_join(main, 
#             df_demo,
#             by = "ID")
# 
# main_single_hr <- 
#   main_single_hr %>% 
#   dplyr::select("time", "heart_rate", "ID", "time_span") %>% 
#   distinct() %>% 
#   group_by(ID) %>% 
#   dplyr::summarise(mean_heart = mean(heart_rate),
#             sd_heart = sd(heart_rate)) %>%
#   ungroup() %>% 
#   right_join(x = .,
#              y = main,
#              by = "ID") %>% 
#   filter(!(time_span == "teaching" & time > 600)) %>%
#   mutate(heart_rate_std = (heart_rate - mean_heart)/
#            sd_heart)

@@

# Multiple Linear Regression (Mean) -- LOOP
```{r}
main %>% 
  group_by(ID, time_span) %>% 
  summarise(disruption_factor = mean(disruption_factor,
                                     na.rm = T),
            confidence_factor = mean(confidence_factor,
                                     na.rm = T),
            teaching_experience = mean(teaching_experience),
            heart_rate = mean(heart_rate_std)
            ) %>% 
  ungroup() -> data_regression_mean

>>>>

# merge two data frames by ID 
df_merge <- merge(df_demo,
                  df_rating,
                  by = "ID") %>% 
  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
                    "132",
                    "236")
         )

@@

# single bpm values (data frame with only single measurement point)
main_single_hr <-
map(.x = dir(path = data_path,
             pattern = ".csv"),
    ~ read_csv(file.path(data_path, .), 
               id = "id",
               col_types = c("t","n")
               ) %>% 
  mutate(time = .$Time - min(.$Time),
         time = as.numeric(time),
         heart_rate = `Heart Rate`,
         ID = id,
         time_span = case_when(str_detect(string = id, pattern = "_a") ~ "end",
                               str_detect(string = id, pattern = "_m") ~ "teaching",
                               str_detect(string = id, pattern = "_p") ~ "preparation",
                               str_detect(string = id, pattern = "_s") ~ "post",
                               str_detect(string = id, pattern = "_i") ~ "interview",
                               TRUE ~ "overall"
                               ),
         ID = str_extract(string = ID,
                          pattern = "[:digit:]{3}"),
         ID = as.numeric(ID)
      ) %>%
    # filter(time <= 600) %>% # filter for 10min intervals
    filter(time <= 7200) %>% # filter for 2 hours (maximal duration of study)
    dplyr::select(!c("Time","Heart Rate","id"))
    ) %>%
  bind_rows()

# adding z-standardized HR
main_single_hr <-
  main_single_hr %>%
  dplyr::select("time", "heart_rate", "ID", "time_span") %>%
  distinct() %>%
  group_by(ID) %>%
  dplyr::summarise(mean_heart = mean(heart_rate),
            sd_heart = sd(heart_rate)) %>%
  ungroup() %>%
  right_join(x = .,
             y = main_single_hr,
             by = "ID") %>%
  filter(!(time_span == "teaching" & time > 600)) %>%
  mutate(heart_rate_std = (heart_rate - mean_heart)/
           sd_heart)

@@

# Multiple Linear Regression (Mean) -- LOOP
```{r}

# multiple bpm values (merged data frame for multiple regression with multiple measurement points)
main_multiple_hr <-
  left_join(main_single_hr,
            df_merge,
            by = "ID")

main_multiple_hr %>% 
  group_by(ID, time_span) %>% 
  summarise(disruption_factor = mean(disruption_factor,
                                     na.rm = T),
            confidence_factor = mean(confidence_factor,
                                     na.rm = T),
            teaching_experience = mean(teaching_experience),
            heart_rate = mean(heart_rate_std)
            ) %>% 
  ungroup() -> data_regression_mean
